A practical look at genetic algorithms

### 2015-11-17 evolutionaryComputation/practicals/report.tex
added about unit tests

Other options I considered were:
\begin{itemize}
	\item Java, which I'm very familiar with but I find quite boring to use.
		Its very verbose.
	\item C\#, the language is good but setting it up is difficult since I
		use Linux, it also has no Gradle support which makes it clunky,
		you'd have to rely on .net libraries only which is limited. It
		also prefers object orientated  rather than functional programming,
		Scala prefers functional over object orientated.
		Scala's syntax is also more concise.
	\item Rust/Go, I'm curious about both these languages, but I'm not at
		all familiar with them, so I probably should do first a little
		hobby project with them before starting doing something serious like
		this, I've already done this with scala before.
\end{itemize}
\subsection{Architecture}
The architecture was created incrementally, I just implemented the functions
without thinking much about how to combine them.  I first started with the
fittest functions. Then I went on with selection, and finally I did the
crossover.
I just implemented one or 2 options of these and then created an evolution
class that accepted functions with the right prototype. So now you can
create an evolution by giving it functions.

>>>>

Other options I considered were:
\begin{itemize}
	\item Java, which I'm very familiar with but I find quite boring to use.
		Its very verbose.
	\item C\#, the language is good but setting it up is difficult since I
		use Linux, it also has no Gradle support which makes it clunky,
		you'd have to rely on .net libraries only which is limited. It
		also prefers object orientated  rather than functional programming,
		Scala prefers functional over object orientated.
		Scala's syntax is also more concise.
	\item Rust/Go, I'm curious about both these languages, but I'm not at
		all familiar with them, so I probably should do first a little
		hobby project with them before starting doing something serious like
		this, I've already done this with Scala before.
\end{itemize}
\subsection{Architecture}
The architecture was created incrementally, I just implemented the functions
without thinking much about how to combine them.  I first started with the
fittest functions. Then I went on with selection, and finally I did the
crossover.
I just implemented one or 2 options of these and then created an evolution
class that accepted functions with the right prototype. So now you can
create an evolution by giving it functions.

\subsubsection{Unit tests}
Because the assignment has very well defined behavior. I thought it was
a very wise Idea to use unit tests. To do this I use a library called
Scala test.
